Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-26 doc/ecp/pres.tex
Updated presentation.

\title[MCREX]{Using Monte Carlo Algorithms to Achieve Resiliency \& Performance
  at Scale for Linear and Nonlinear Solver Applications}
\author{Thomas Evans \and Steven Hamilton}
\date[DOE, 2016]{DOE RX-Solvers \\ January 29, 2016}
\institute[ORNL]{Oak Ridge National Lab}

@@

@@

@@

  \underline{\bf XPRESS}
  \begin{itemize}
  \item We are currently implementing a CUDA transport kernel with scheduling
    optimized by HPX as part of XPRESS
  \item We have already compared OpenMP versus HPX for on-node MC particle
    transport algorithms
  \end{itemize}

  \begin{figure}
    \centering
    \begin{tabular}{cc}
      \subfigure[time]{\includegraphics[width=2in]{time}}
      &
      \subfigure[efficiency]{\includegraphics[width=2in]{tallies}}
    \end{tabular}
  \end{figure}

>>>>

\title[MCREX]{Using Monte Carlo Algorithms to Achieve Resiliency \& Performance
  at Scale for Linear and Nonlinear Solver Applications}
\author{Thomas Evans (PI, ORNL)\\
  Michele Benzi (Co-PI, Emory)\\
  Steven Hamilton (ORNL)\\
  Stuart Slattery (ORNL)\\
  Christian Engelmann (ORNL)\\
  Wayne Joubert (ORNL)\\
  Massimiliano Lupo Pasini (Emory)
}
\date[DOE, 2016]{DOE RX-Solvers, 1/29/2016}
%\institute[ORNL]{Oak Ridge National Lab}

@@

%%---------------------------------------------------------------------------%%
\subsection{ECP R\&D}
%%---------------------------------------------------------------------------%%

@@

%%---------------------------------------------------------------------------%%
\subsection{Building on ASCR Funding}
%%---------------------------------------------------------------------------%%

@@

  \underline{\bf XPRESS}
  \begin{itemize}
    \setlength{\itemsep}{-0.1\baselineskip}
  \item We are currently implementing a CUDA transport kernel with scheduling
    optimized by HPX as part of XPRESS
  \item We have already compared OpenMP versus HPX for on-node MC particle
    transport algorithms
    \begin{figure}
      \centering
      \begin{tabular}{cc}
        \subfigure[time]{\includegraphics[width=1.8in]{time}}
        &
        \subfigure[efficiency]{\includegraphics[width=1.8in]{tallies}}
      \end{tabular}
    \end{figure}
  \item All code implementations are available in the open source Profugus
    mini-app (\underline{github.com/ORNL-CEES/Profugus})
  \end{itemize}
